The Chemistry Development Kit (CDK) \cdkversion{}: atom typing, depiction, molecular formulas, and substructure searching

### 2017-05-02 article.tex
proofing

  While the API itself has not been significantly changed, the
  internals have been revamped. In addition to improved overlap
  resolution noted above, the engine appropriately handles large ring
  systems, maintains input stereochemistry, and makes use of a large
  template library. Templates are useful for laying out substructure
  While previous CDK versions partially supported 
  double bond stereochemistry the new engine is more efficient in
  using this information when generate 2D layouts. Furthermore, the
  engine assigns wedge bond information based on tetrahedral
  stereochemistry. These features are exemplified by the following
  code and the resulting layout depiction in
  Figure~\ref{fig:sdgstereo}:

@@

Originally, the CDK was developed as a shared library between
JChemPaint~\cite{krause2000jchempaint} and
Jmol~\cite{Willighagen2007jmol,Hanson2010}.  JChemPaint used a MVC
approach with an event-passing mechanism to update the view when the
model was changed. This can cause an cascade of change events being
passed around. This was not always a desirable feature, especially for
non-UI code. To address this, interfaces were introduced allowing
multiple implementations of the core interfaces. With much code of the CDK
library no longer based on the original data model, a builder is needed to
create objects of that data model, such as an implementation of the IAtom.
The new \texttt{IChemObjectBuilders} allow implementations to be created, allowing
implementations of the interfaces to be instantiated without the need
of explicitly referencing those implementations. This way, any algorithm
implementation in the CDK can use any of the data model interface
implementations.

>>>>

  While the API itself has not been significantly changed, the
  internals have been revamped. In addition to improved overlap
  resolution noted above, the engine appropriately handles large ring
  systems, maintains input stereochemistry, and makes use of a large
  template library. Templates are useful for laying out substructure.
  While previous CDK versions partially supported 
  double bond stereochemistry the new engine is more efficient in
  using this information when generating 2D layouts. Furthermore, the
  engine assigns wedge bond information based on tetrahedral
  ste\-reo\-chem\-is\-try. These features are exemplified by the following
  code and the resulting layout depiction in
  Figure~\ref{fig:sdgstereo}:

@@

Originally, the CDK was developed as a shared library between
JChemPaint~\cite{krause2000jchempaint} and
Jmol~\cite{Willighagen2007jmol,Hanson2010}.  JChemPaint used a MVC
approach with an event-passing mechanism to update the view when the
model was changed. This can cause a cascade of change events being
passed around. This was not always a desirable feature, especially for
non-UI code. To address this, interfaces were introduced allowing
multiple implementations of the core interfaces. With much code of the CDK
library no longer based on the original data model, a builder is needed to
create objects of that data model, such as an implementation of the IAtom.
The new \texttt{IChemObjectBuilders} allow implementations to be created, allowing
implementations of the interfaces to be instantiated without the need
of explicitly referencing those implementations. This way, any algorithm
implementation in the CDK can use any of the data model interface
implementations.
